\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{tgheros}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.5em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{center}
  {\Large \textbf{Anthony Orrico}} \\[4pt]
  \href{https://www.linkedin.com/in/anthony-orrico-b78341157/}{linkedin.com/in/anthony-orrico} \quad$|$\quad
  New York, NY 10005 \quad$|$\quad
  (732) 325-7344 \quad$|$\quad
  aorrico2@gmail.com
\end{center}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Morgan Stanley}{New York, NY}
      {Director / Tech Lead -- Institutional Securities Tech -- Full Stack Developer}{Mar 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Own core services supporting a distributed data platform composed of No SQL databases, Kafka messaging, real time ingestion pipelines and Spring based APIs.}
        \resumeItem{Overhauled bond reference data cleaning workflows used by real time trading systems, improving data accuracy and operational reliability.}
        \resumeItem{Improved high priority Bloomberg data ingestion pipelines, reducing processing latency by more than 5x.}
        \resumeItem{Modernized legacy Spring services through large scale upgrades across major Spring, Gradle, and JDK versions, improving maintainability and stability.}
        \resumeItem{Drove adoption of automated SDLC workflows and developer tooling initiatives across the department.}
        \resumeItem{Managed and enhanced a high impact loan pricing platform (backend and frontend) supporting trading operations and internal users.}
        \resumeItem{Automated pricing export and data processing for trading desks, reducing turnaround time from 1 week to under 4 hours.}
        \resumeItem{Built backend services for ETF trade booking dashboard utilizing Python Tornado, PostgresSQL database design, and CPS real time messaging.}
        \resumeItem{Introduced AI assisted workflows using GitHub Copilot CLI to improve engineering productivity across backend and frontend development.}
      \resumeItemListEnd

    \resumeSubheading
      {Morgan Stanley}{New York, NY}
      {Associate -- Institutional Securities Tech -- Full Stack Developer}{Aug 2021 -- Mar 2024}
      \resumeItemListStart
        \resumeItem{Owned and operated a large-scale Mongo DB + Elasticsearch cache housing reference data for 30+ million bonds.}
        \resumeItem{Led containerization and streamlined workflows for 70+ distributed Spring services and ingestion processes using Docker.}
        \resumeItem{Automated Ready for Business checks to ensure the highest data quality for real time trading users.}
        \resumeItem{Designed and implemented batch and streaming data loaders using Java Spring from REST APIs, CPS messaging systems, files, No SQL databases, and Sybase/KDB sources.}
        \resumeItem{Created internal data merging and stored procedure frameworks that simplified onboarding and customization for downstream consumers.}
        \resumeItem{Spearheaded development of Angular based tooling for querying and visualizing bond reference data via AG Grid.}
      \resumeItemListEnd

    \resumeSubheading
      {Morgan Stanley}{New York, NY}
      {Technology Analyst Internship -- Institutional Securities Tech -- Backend Developer}{Jun 2020 -- Aug 2020}
      \resumeItemListStart
        \resumeItem{Built Java Spring services to capture and monitor application usage metrics.}
        \resumeItem{Leveraged Apache Kafka and Elasticsearch pipelines for real time analytics and operational monitoring.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Morgan Stanley Technology Analyst Program}{New York, NY}
      {Graduated from Morgan Stanley's rigorous 10 week Backend Developer Training Bootcamp}{Aug 2021 -- Nov 2021}
    \resumeSubheading
      {Stevens Institute of Technology}{Hoboken, NJ}
      {Master of Engineering - Applied Artificial Intelligence}{Aug 2020 -- May 2021}
    \resumeSubheading
      {Stevens Institute of Technology}{Hoboken, NJ}
      {Bachelor of Engineering with High Honor in Computer Engineering, Minor in Computer Science}{Aug 2016 -- May 2020}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item \small{\textbf{Languages:} Java, Python, TypeScript, JavaScript, SQL, Scala} \vspace{-4pt}
    \item \small{\textbf{Frameworks \& Systems:} Spring, Project Reactor (Flux), Elasticsearch, Mongo DB, Tornado, Angular, Distributed Systems, Real-Time Data Pipelines, Batch \& Stream Processing} \vspace{-4pt}
    \item \small{\textbf{Infrastructure \& Tools:} Kafka, CPS/MQ, Docker, Node.js, Git, Google Protobuf, Sybase/Postgres/KDB, OpenTelemetry, CI/CD}
  \resumeSubHeadingListEnd

\end{document}
